\mytitle

### 2015-08-05 MSc_diss.tex
Updates in figures (all in .eps)

\documentclass[11pt,a4paper]{article}
% Font
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
% Encoding and language
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
% Colors
\usepackage[usenames,dvipsnames]{color}
\usepackage{colortbl}
% Paper size and margins
%\usepackage{rotating}
\usepackage{pdflscape}
%\usepackage[a4paper,showframe]{geometry}
\usepackage{vmargin}
\setmarginsrb{2cm}{2cm}{2cm}{2cm}{0cm}{0cm}{0cm}{1.5cm}
\usepackage{pdflscape}
\usepackage{afterpage}
% Indenting and line spacing
\linespread{1.5}
%\usepackage{setspace}
\usepackage{indentfirst}
%\setlength{\parindent}{1cm}
\setlength{\parskip}{0.5cm}
% Symbols
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
% Equations
\usepackage{eulervm} % upright font in eqns (Palatino)
\usepackage{cool}
\usepackage{mathtools} % for arrows

@@

% References
\usepackage{natbib}
\bibliographystyle{apalike}
% Hyperlinks and labels
%\usepackage{showkeys}
\usepackage[linktocpage=true,plainpages=false,pdfpagelabels=false]{hyperref}
\definecolor{citecolor}{rgb}{0.2,0.7,0.9}
\definecolor{urlcolor}{rgb}{0,0,1}
\hypersetup{
    colorlinks, linkcolor={Blue},
    citecolor={Blue}, urlcolor={Black}
}
% Figures
\usepackage{subcaption}
\usepackage{alphalph}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usepackage{epstopdf}
\usepackage{wrapfig}
% Tables
\usepackage{multirow}
% Tikz styles
\tikzstyle{reg} = [rounded rectangle, text width=2cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{rad} = [rounded rectangle, draw=none, text width=2cm, fill=red!10, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{long} = [rounded rectangle, draw=none, text width=3.5cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]   
\tikzstyle{add} = [scale=1.5, draw=none,fill=none,align=center]
\tikzstyle{emp} = [draw=none,fill=none]
\tikzstyle{ar} = [->,draw=black!70,line width=2]
\tikzstyle{ln} = [-,draw=black!70,line width=2]
% Title etc
\newcommand{\mytitle}{Investigation of the relationship between tropospheric ozone production efficiency and carbon bond emissions}
\newcommand{\authorname}{Maria Zamyatina}
\newcommand{\authornumber}{Student No: 100106685}
\newcommand{\degname}{Master of Science}
\newcommand{\univname}{University of East Anglia}
\newcommand{\univaddr}{University Plain \\ Norwich NR47TJ UK}
\newcommand{\depname}{School of Environmental Sciences}
\newcommand{\mydate}{\the\year}

@@

\begin{abstract}
Abstract.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\arraystretch}{1}
\begin{table}[h!]
\caption{!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}\label{tab:ANmean} % mean AN mixing ratios
\begin{tabular}{cccc}
\hline
Environment     & Mean $\Sigma RONO_2$ & $\Sigma RONO_2$ breakdown & Reference \\
\hline
remote marine   & 10 pptv    & methyl                   & \citep{Reeves2007} \\
(North Atlantic)&            & ethyl                    & \\
airborne        &            & 1-propyl                 & \\   
                             && 2-propyl                & \\   
                             && 2-butyl                 & \\                                                                                               
                             && 2-methyl-3-butyl        & \\
                             && sum of 2- and 3-pentyl  & \\
\hline
rural           & 14 pptv    & methyl                   & \citep{Roberts1998} \\
(Nova Scotia, Canada)        && ethyl   & \\
ground                       && n-propyl & \\
                             && 2-propyl & \\
                             && 2-butyl  & \\ 
\hline
suburban                     & 17.48 pptv  & 2-propyl    & \citep{DeKock1994} \\
(Cape Retire, South Africa)  &(3.62-122.23)& 1-propyl & \\
ground                                    && 2-butyl  & \\
                                          && 1-butyl  & \\
                                          && 3-pentyl & \\
                                          && 2-pentyl & \\
                                          && 2-methyl-1-butyl & \\
                                          && i-pentyl & \\
\hline
suburban                     & 119.8 ppt  & $C_1$-$C_8$       & \citep{Flocke1998} \\
(Black Forest, Germany)      & (30-630 ppt) && \\ 
ground                                     &&& \\
\hline
polluted marine & approx 1 ppb & $NO_y$-($NO_x$+$HNO_3$+$PAN$) & \citep{Neuman2012} \\
(Gulf of Mexico)&(plume center) && \\
airborne &&& \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

As it has been noted in Section \ref{sec:intro}, the relationship between $O_3$ and $RONO_2$ production rates is controlled by the branching ratio ($\alpha_3$) between reactions:
\begin{equation}
RO_2 + NO \xrightarrow{1-\alpha_3} RO + NO_2\tag{\ref{reac:RO2+NO=aphaRO+NO2}}
\end{equation}
\begin{equation}
RO_2 + NO \xrightarrow{\alpha_3} RONO_2\tag{\ref{reac:RO2+NO=aphaRONO2}}
\end{equation}
Reaction (\ref{reac:RO2+NO=aphaRO+NO2}) leads to $O_3$ production and $NO$ regeneration, resulting in continuing $O_3$ production, while reaction (\ref{reac:RO2+NO=aphaRONO2}) terminates this process. Branching ratios used in the model are taken from the MCM v3.3, and their values (Table \ref{tab:ANbranching}) were kept constant in all model runs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} %  AN branching ratios
\caption{Branching ratios for the formation of alkyl nitrates from their precursor peroxy radicals and $NO$ (taken from the MCM v3.3 (2015)).}\label{tab:ANbranching}
\centering
\begin{tabular}{cc}
\hline
Alkyl nitrate    & Branching ratio \\
\hline
methyl           & 0.001 \\
ethyl            & 0.009 \\
iso-propyl       & 0.042 \\
n-propyl         & 0.020 \\
n-butyl          & 0.033 \\
sec-butyl        & 0.090 \\
iso-butyl        & 0.033 \\ 
tert-butyl       & 0.025 \\
n-pentyl         & 0.052 \\
2-pentyl         & 0.129 \\
3-pentyl         & 0.131 \\
2-methylbutyl    & 0.052 \\
3-methyl-2-butyl & 0.141 \\
2-methyl-2-butyl & 0.047 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3rate noAN withAN diff
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3rate_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3ratediff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:netO3rate_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % netO3mixrat noAN allAN diff diffpercent
\centering
\begin{minipage}{.4\textwidth} % noAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diff
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiff_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % allAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.4\textwidth} % diffpercent
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiffpercent_noINORG_NOx_250ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net $O_3$ production (ppb, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb, range 250 ppt - 100 ppb) with alkyl nitrate chemistry switched off (a) and switched on (b). Absolute difference (with alkyl nitrates minus without them) between two series of model runs in ppb (c), same in \% (d). Net production = final - initial value of $O_3$ mixing ratio.}\label{fig:netO3mixrat_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % endtotalANs
\includegraphics[width=.5\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_endtotalANs_noINORG_NOx_250ppt_100ppb.png}
\caption{Isopleths of net production of alkyl nitrates ($\Sigma RONO_2$) as a function of $NO_x$ and $VOCs$ levels.}\label{fig:endtotalANs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
! Dependence of alkyl nitrate yield on carbon number (paper about n-alkanes): bigger yield of ANs from larger carbon number means that the potential for contributing to photochemical air pollution may be less for the larger (C>6) n-alkanes that for the smaller ones.

>>>>

\documentclass[11pt,a4paper]{article}
% Font
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
% Encoding and language
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
% Colors
\usepackage[usenames,dvipsnames]{color}
\usepackage{colortbl}
% Paper size and margins
%\usepackage{rotating}
\usepackage{pdflscape}
%\usepackage[a4paper,showframe]{geometry}
\usepackage{vmargin}
\setmarginsrb{2.5cm}{2cm}{2.5cm}{2cm}{0cm}{0cm}{0cm}{1.5cm}
\usepackage{pdflscape}
\usepackage{afterpage}
% Indenting and line spacing
\linespread{1.5}
%\usepackage{setspace}
\usepackage{indentfirst}
%\setlength{\parindent}{1cm}
\setlength{\parskip}{0.5cm}
% Symbols
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
% Equations
\usepackage{eulervm} % upright font in eqns (Palatino)
\usepackage{cool}
\usepackage{mathtools} % for arrows

@@

% References
\usepackage{natbib}
\bibliographystyle{apalike}
% Hyperlinks and labels
%\usepackage{showkeys}
\usepackage[linktocpage=true,plainpages=false,pdfpagelabels=false]{hyperref}
\definecolor{citecolor}{rgb}{0.2,0.7,0.9}
\definecolor{urlcolor}{rgb}{0,0,1}
\hypersetup{
    colorlinks, linkcolor={Blue},
    citecolor={Blue}, urlcolor={Black}
}
% Figures
\usepackage{subcaption}
\usepackage{alphalph}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usepackage{epstopdf}
\usepackage{wrapfig}
% Tables
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
% Tikz styles
\tikzstyle{reg} = [rounded rectangle, text width=2cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{rad} = [rounded rectangle, draw=none, text width=2cm, fill=red!10, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{long} = [rounded rectangle, draw=none, text width=3.5cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]   
\tikzstyle{add} = [scale=1.5, draw=none,fill=none,align=center]
\tikzstyle{emp} = [draw=none,fill=none]
\tikzstyle{ar} = [->,draw=black!70,line width=2]
\tikzstyle{ln} = [-,draw=black!70,line width=2]
% Title etc
\newcommand{\mytitle}{Investigation of the relationship between tropospheric ozone production efficiency and carbon bond emissions}
\newcommand{\authorname}{Maria Zamyatina}
\newcommand{\authornumber}{Student No: 100106685}
\newcommand{\degname}{Master of Science}
\newcommand{\univname}{University of East Anglia}
\newcommand{\univaddr}{University Plain \\ Norwich NR47TJ UK}
\newcommand{\depname}{School of Environmental Sciences}
\newcommand{\mydate}{\the\year}

@@

\begin{abstract}
Abstract.300 words.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\arraystretch}{1}
\begin{table}[h!]
\caption{!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}\label{tab:ANmean} % mean AN mixing ratios
\begin{tabularx}{\linewidth}{P{3cm}P{2cm}P{5cm}X}
\hline
Environment     & Mean $\Sigma RONO_2$ & $\Sigma RONO_2$ breakdown & Reference \\
\hline
remote marine (North Atlantic), airborne   & 10 pptv    & methyl, ethyl, 1-propyl, 2-propyl, 2-butyl, 2-methyl-3-butyl, sum of 2- and 3-pentyl  & \citep{Reeves2007} \\
\hline
rural ground (Nova Scotia, Canada)        & 14 pptv    & methyl, ethyl, n-propyl, 2-propyl, 2-butyl  & \citep{Roberts1998} \\
\hline
suburban ground (Cape Retire, South Africa)  & 17.48 pptv (3.62-122.23) & 2-propyl, 1-propyl, 2-butyl, 1-butyl, 3-pentyl, 2-pentyl, 2-methyl-1-butyl, i-pentyl & \citep{DeKock1994} \\
\hline
suburban ground (Black Forest, Germany)    & 119.8 ppt (30-630 ppt) & $C_1-C_8$ & \citep{Flocke1998} \\
\hline
polluted marine airborne (Gulf of Mexico) & approx 1 ppb (plume center)& $NO_y-(NO_x+HNO_3+PAN)$ & \citep{Neuman2012} \\
\hline
\end{tabularx}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

As it has been noted in Section \ref{sec:intro}, the relationship between $O_3$ and $RONO_2$ production rates is controlled by the branching ratio ($\alpha_3$) between reactions:
\begin{equation}
RO_2 + NO \xrightarrow{1-\alpha_3} RO + NO_2\tag{\ref{reac:RO2+NO=aphaRO+NO2}}
\end{equation}
\begin{equation}
RO_2 + NO \xrightarrow{\alpha_3} RONO_2\tag{\ref{reac:RO2+NO=aphaRONO2}}
\end{equation}
Reaction (\ref{reac:RO2+NO=aphaRO+NO2}) leads to $O_3$ production and $NO$ regeneration, resulting in continuing $O_3$ production, while reaction (\ref{reac:RO2+NO=aphaRONO2}) terminates this process. Branching ratios used in the model are taken from the MCM v3.3, and their values (Table \ref{tab:ANbranching}) were kept constant in all model runs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} %  AN branching ratios
\caption{Branching ratios for the formation of alkyl nitrates from their precursor peroxy radicals and $NO$ (taken from the MCM v3.3 (2015)).}\label{tab:ANbranching}
\centering
\begin{tabular}{cc}
\hline
Alkyl nitrate    & Branching ratio \\
\hline
methyl           & 0.001 \\
ethyl            & 0.009 \\
iso-propyl       & 0.042 \\
n-propyl         & 0.020 \\
n-butyl          & 0.033 \\
sec-butyl        & 0.090 \\
iso-butyl        & 0.033 \\ 
tert-butyl       & 0.025 \\
n-pentyl         & 0.052 \\
2-pentyl         & 0.129 \\
3-pentyl         & 0.131 \\
2-methylbutyl    & 0.052 \\
3-methyl-2-butyl & 0.141 \\
2-methyl-2-butyl & 0.047 \\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!] % netO3rate noAN withAN diff
	\centering
	\begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_noINORG_NOx_250ppt_100ppb.eps}
        \caption{}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3rate_noINORG_NOx_250ppt_100ppb.eps}
        \caption{}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3ratediff_noINORG_NOx_250ppt_100ppb.eps}
        \caption{}
    \end{subfigure}%
    \hfill
\caption{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}\label{fig:netO3rate_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h] % netO3mixrat noAN allAN diff diffpercent
\centering
\begin{minipage}{.45\textwidth} % noAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.eps}
\end{minipage}
\begin{minipage}{.45\textwidth} % diff
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiff_noINORG_NOx_250ppt_100ppb.eps}
\end{minipage}
\begin{minipage}{.45\textwidth} % allAN
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixrat_noINORG_NOx_250ppt_100ppb.eps}
\end{minipage}
\begin{minipage}{.45\textwidth} % diffpercent
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3mixratdiffpercent_noINORG_NOx_250ppt_100ppb.eps}
\end{minipage}
\caption{Isopleths giving net $O_3$ production (ppb, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb, range 250 ppt - 100 ppb) with alkyl nitrate chemistry switched off (a) and switched on (b). Absolute difference (with alkyl nitrates minus without them) between two series of model runs in ppb (c), same in \% (d). Net production = final - initial value of $O_3$ mixing ratio.}\label{fig:netO3mixrat_noAN_withAN_diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure} % endtotalANs
\centering
\includegraphics[width=.7\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_endtotalANs_noINORG_NOx_250ppt_100ppb.eps}
\caption{Isopleths of net production of alkyl nitrates ($\Sigma RONO_2$) as a function of $NO_x$ and $VOCs$ levels.}\label{fig:endtotalANs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
! Dependence of alkyl nitrate yield on carbon number (paper about n-alkanes): bigger yield of ANs from larger carbon number means that the potential for contributing to photochemical air pollution may be less for the larger (C>6) n-alkanes that for the smaller ones.
